A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-05 manuscript.Rmd
explain advantages of DOI #38

## Creating a DOI
<!-- AP add references; why are DOIs helpful-->

<!-- public releases like preregistration, preprint -->
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artifacts for research and provides digital object identifiers (DOI) for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.
You may log into zenodo.org through your GitHub account.

>>>>

## Creating a DOI

The approach we advocate for distributes the research project, e.g. across GitHub, preregistration platforms, the publishers site, and more.
Digital Object Identifiers (DOI) tie all these locations together under one link [@derisiWhatWhysDOIs2003].
Not only can a DOI resolve to several locations, several parts of a research project can get their own DOI besides the DOI of the publication.
This is useful to link or cite a specific part of a research project, such as the preregistration, an illustration in the paper or the data that was gathered.
The DOI can also contain information about the license of the object it refers to.
<!-- public releases like preregistration, preprint -->
zenodo.org [@zenodo] is a publicly funded service provider that archives digital artifacts for research and provides doi for these archives.
While the service is independent of GitHub---in terms of storage facilities and financing---you can link GitHub and zenodo.org.
Please note that you can only link public GitHub repositories to zenodo.
You may log into zenodo.org through your GitHub account.
